\section{Related Work}

In this section we summarize prior work related to this project.
This includes work in semi-supervised learning as well as detecting DNS threats.

\subsection{Semi-supervised Learning}

Security is not a new application for machine learning.
Many researchers have attempted to use machine learning for intrusion detection, spam filtering,
or other topics, and have been successful.
However, many of these applications have relied on purely supervised or unsupervised learning techniques.
Semi-supervised learning has only gained popularity in the last few years, but has proven itself
a valuable tool, much more so than purely supervised or unsupervised methods.

A problem with machine learning is the tendency towards false alarms.
This is especially prevalent in unsupervised methods.
Intrusion detection is the most logical application of machine learning in the field of security.
A system is best when it can detect both known threats and unknown threats.
This requires unsupervised learning to detect the unknown threats, but can easily result in false alarms.
In Chiu \etal{}, they combatted false alarms in the Snort Intrusion Detection System (IDS), and were
able to reduce the false alarm rate by $85\%$ using semi-supervised learning~\cite{semialarm}.
In Chen \etal{}, the researchers proved that semi-supervised algorithms of their creation are able
to outperform both supervised and unsupervised methods~\cite{semidetect}.
It is also proven in Wang \etal{} that network traffic clustering is significantly improved using
semi-supervised learning~\cite{seminovel}.

\subsection{DNS Threat Detection}

There has been a significant amount of work in detecting DNS threats over the years, but very few
involve machine learning, if any.
The closest work in existence are non-learning oriented detection methods.

\subsubsection{Cyber Squatting}

Cyber squatting is a problem that is hard to combat.
It is not illegal to register domain names that are similar to the names of trademarked names.
It is also not easily detectable outside of using a black list.
This is tedious and ineffective against unknown malicious names.
In Chen \etal{}, the researchers were able to devise a browser extension that would warn users of
possible typing mistakes.
They named their system ATST, and found that it was able to detect up to $85\%$ of user errors.
It was also fast, delivering responses in as little as $300$ milliseconds~\cite{squat}.
Other systems for detection are built for website owners rather than end users.
Microsoft's Strider~\cite{strider}, Veralab's tool~\cite{veralab}, and dnstwist~\cite{elceef} are
all tools that a site owner can use to generate possible typo errors in their site names and check
if domains are registered under those names.\
dnstwist is the most recent and is quite effective.
However, none of these serve a purpose for detection on the user end.

\subsubsection{Generated Names}

\subsubsection{Tunneling}

